\vspace{60pt}\\ \huge \bfseries SKEDGE \\ \vspace{10pt} \Large Smarter course scheduling for our\\ University of Rochester

### 2016-04-10 design.tex
More design

\section{Search}

Of course, the most important usability concern for a course explorer/scheduler is effectively \emph{finding courses}.

First, I will list some of the criteria students have for finding courses and how Skedge improves

@@

%Figure

See the appendix for a full list of these natural language things.

  \subsubsection{Advantages}

@@

  \subsubsection{Disadvantages}
  grammar ambiguities (can be solved with a `did you mean')

@@

\section{Social}

@@

\subsection{Skedge Social}

>>>>

\section{Search friendliness}

Of course, the most important usability concern for a course explorer/scheduler is being able to effectively \emph{find courses}.

In this section, I will present the \emph{Skedge DSQL}, a domain-specific query language that is based on natural language. Next, I will demonstrate how Skedge leverages the DSQL to handle the three search criteria students have for finding courses better than CDCS does.

@@

In the spirit of this chapter's theme, Skedge's search method was, again, primarily designed as a reaction to CDCS's. CDCS's search method is a 15-field form (see Figure \ref{fig:cdcs-search}), of which I only found myself regularly using two (one of them being the \emph{required} ``Year/Term'' field). This prompted me to closely examine the fields to a) determine redundancies between them and b) find how to make some of the valuable filter fields more usable. From this came Skedge's unified, natural language based search method, which I call the \emph{Skedge Domain-Specific Query Language (Skedge DSQL)}. Figure \ref{fig:sk-search} is a list of example possible searches shown to users as they type.

\begin{figure}[ht]
  \centering
  \vspace{5pt}
  \begin{tabular}{c c}
    \begin{subfigure}[w]{4.5cm}
      \centering
      \fbox{
        \includegraphics[width=3.3cm]{images/cdcs/search}
      }
      \caption{Form-based search in CDCS} \label{fig:cdcs-search}
    \end{subfigure}
    \hspace{5pt}
    \begin{subfigure}[w]{8.5cm}
      \centering
      \fbox{
        \includegraphics[width=1.00\textwidth]{images/skedge/search}
      }
      \caption{Examples of the Skedge DSQL} \label{fig:sk-search}
    \end{subfigure}
  \end{tabular}
  \caption{Two philosophies of search method}
\end{figure}

\begin{figure}[ht]
  \centering
  \vspace{10pt}
  \includegraphics[width=12cm]{images/search-mapping}
  \caption{Mapping from CDCS's form-based search to the Skedge DSQL} \label{fig:search-mapping}
\end{figure}

Figure \ref{fig:search-mapping} is a mapping of each CDCS field to an element of the Skedge DSQL.

  \subsubsection{Advantages of the DSQL}

@@

  \subsubsection{Disadvantages of the DSQL}
  grammar ambiguities (can be solved with a `did you mean')

@@

\section{``Skedge Social''}

@@

\subsection{Skedge's solution}

### 2016-04-10 paper.tex
More design

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually pleasing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that a) Skedge's differences from and additions to CDCS are usable and have real need, b) the two major use-cases associated with course browsing---direct search and exploratory search---are effectively accommodated by Skedge, and c) Skedge's search mechanism is user-friendly and self-teaches to users over time.

>>>>

In this paper I present Skedge, a web application for students to comfortably and effectively engage with the University's course catalog. Skedge matches and surpasses the capabilities of the existing University tool for this purpose, ``Course Description / Course Schedule'' (CDCS) and presents its information in a more visually pleasing way. As a result, Skedge boasts strong user-retention rates, long session durations, and high student adoption despite having virtually no advertisement. Through collected usage data, I demonstrate that \textbf{a)} Skedge's differences from and additions to CDCS are usable and have real need, \textbf{b)} the three major use-cases associated with course browsing---direct search, exploratory search, and peer recommendation---are effectively accommodated by Skedge, and \textbf{c)} Skedge's search mechanism is user-friendly and self-teaches to users over time.
